### 2014-06-03 talk/dls2014/paper/paper.tex
the term "bump-pointer" seems to be the much more common one

However, the layout of a segment is not uniform and we actually
privatise a few areas again right away. These areas are illustrated in
Figure~\ref{fig:Segment-Layout} and explained here:
\begin{description}[noitemsep]
\item [{NULL~page:}] This page is unmapped and will produce a
  segmentation violation when accessed. We use this to detect
  erroneous dereferencing of \lstinline!NULL! references.  All
  $\%gs{::}SO$ translated to linear addresses will point to NULL pages
  if $SO$ is set to \lstinline!NULL!.
\item [{Segment-local~data:}] Some area private to the segment that
  contains segment-local information.
\item [{Read~markers:}] These are pages that store information about
  which objects were read in the current transaction running in this
  segment.
\item [{Nursery:}] This area contains all the freshly allocated
  objects (\emph{young objects}) of the current transaction. The GC
  uses pointer-bump allocation in this area to allocate objects in the
  first generation.
\item [{Old~object~space:}] These pages are the ones that are really
  shared between segments. They mostly contain old objects but also
  some young ones that were too big to be allocated in the nursery.
\end{description}

@@

@@

This code does simple pointer-bump allocation in the nursery. If there
is still space left in the nursery, we return
\lstinline!nursery_current!  and bump it up by
\lstinline!size_rounded!.  The interesting part is the check
\lstinline!nursery_current > nursery_end!  which will trigger the slow
path of the function to possibly perform a minor collection in order
to free up space in the nursery.

>>>>

However, the layout of a segment is not uniform and we actually
privatise a few areas again right away. These areas are illustrated in
Figure~\ref{fig:Segment-Layout} and explained here:
\begin{description}[noitemsep]
\item [{NULL~page:}] This page is unmapped and will produce a
  segmentation violation when accessed. We use this to detect
  erroneous dereferencing of \lstinline!NULL! references.  All
  $\%gs{::}SO$ translated to linear addresses will point to NULL pages
  if $SO$ is set to \lstinline!NULL!.
\item [{Segment-local~data:}] Some area private to the segment that
  contains segment-local information.
\item [{Read~markers:}] These are pages that store information about
  which objects were read in the current transaction running in this
  segment.
\item [{Nursery:}] This area contains all the freshly allocated
  objects (\emph{young objects}) of the current transaction. The GC
  uses bump-pointer allocation in this area to allocate objects in the
  first generation.
\item [{Old~object~space:}] These pages are the ones that are really
  shared between segments. They mostly contain old objects but also
  some young ones that were too big to be allocated in the nursery.
\end{description}

@@

\cfbolz{you need to describe when and how to re-share pages}

@@

This code does simple bump-pointer allocation in the nursery. If there
is still space left in the nursery, we return
\lstinline!nursery_current!  and bump it up by
\lstinline!size_rounded!.  The interesting part is the check
\lstinline!nursery_current > nursery_end!  which will trigger the slow
path of the function to possibly perform a minor collection in order
to free up space in the nursery.

### 2014-06-03 talk/icooolps2009-dotnet/clibackend.tex
last minute fix
the term "bump-pointer" seems to be the much more common one

It is important to underline the difference between flow graphs and a methods:
the first are the logical unit of code as seen by the JIT compiler, each of
them being concretely implemented by \emph{one or more} methods.

@@

To implement each flexswitch, the CLI backend creates an instace of a subclass
of \lstinline{BaseLowLevelFlexSwitch}: such an instance stores the mapping
between each value and the corresponding method we want to invoke.  Then, the
generated code contains a call to the method \lstinline{execute}, which
selects and invoke the right method depending on the actual value we are
switching on.

The following snippet shows the special case of integer flexswitches.
\begin{lstlisting}[language={[Sharp]C}] 
public class IntLowLevelFlexSwitch: 
                        BaseLowLevelFlexSwitch {
  public uint default_blockid = 0xFFFFFFFF;
  public int numcases = 0;
  public int[] values = new int[4];
  public FlexSwitchCase[] cases = 
                          new FlexSwitchCase[4];

>>>>

It is important to underline the difference between flow graphs and methods:
the first are the logical unit of code as seen by the JIT compiler, each of
them being concretely implemented by \emph{one or more} methods.

@@

To implement each flexswitch, the CLI backend creates an instance of a subclass
of \lstinline{BaseLowLevelFlexSwitch}: such an instance stores the mapping
between each value and the corresponding method we want to invoke.  Then, the
generated code contains a call to the method \lstinline{execute}, which
selects and invoke the right method depending on the actual value we are
switching on.

The following snippet shows the special case of integer flexswitches:
\begin{lstlisting}[language={[Sharp]C}] 
public class IntLowLevelFlexSwitch: 
                        BaseLowLevelFlexSwitch {
  public uint default_blockid = 0xFFFFFFFF;
  public int numcases = 0;
  public int[] values = new int[4];
  public FlexSwitchCase[] cases = 
                          new FlexSwitchCase[4];
